High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-19 paper/main.tex
update figure with new ordered up to correlations (up to 15)

We repeated this process for each set of parameters, varying kernel
type and width, and averaged over the reduction technique used to
approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
centrality Fig.~\ref{fig:decoding_level},  d.-f.).  Since there is no ground truth in these analyses, and we did not know
which parameters best capture the data, we instead report a robustness
search by averaging over the parameters and reporting which results
consistently showed up across all parameters.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/brain_plots.pdf}
  \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
    centrality to approximate higher-order correlations for \textbf{a.-d. intact, e.-h. paragraph scrambled,
      i.-l. word scrambled, and m.-p. rest } conditions, we plot the
    strongest 25\% absolute value
    mean correlation for first through fourth orders, representing the degree of agreement by
    location pair over time.}
  \label{fig:brain_plots}
\end{figure}

>>>>

We repeated this process for each set of parameters, varying kernel
type and width, and averaged over the reduction technique used to
approximate the higher-order correlations (PCA Fig.~\ref{fig:decoding_level},  a.-c. and eigenvector
centrality Fig.~\ref{fig:decoding_level},  d.-f.).  Since there is no ground truth in these analyses, and we did not know
which parameters best capture the data, we instead report a robustness
search by averaging over the parameters and reporting which results
consistently showed up across all parameters.
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/brain_plots.pdf}
  \caption{\textbf{Average correlations by order for the intact listening condition.} Using eigenvector
    centrality to approximate higher-order correlations for the
    intact, paragraph scrambled, word scrambled, and rest condition.
    We plot the
    strongest 50\% absolute value
    mean correlation for \textbf{a.-d. first order, e.-h. second order,
      i.-l. third order, and m.-p. fourth order }, representing the degree of agreement by
    location pair over time.  To demonstrate how this method is
    computationally scalable, we also approximated
    \textbf{a.-d. fifteenth order} dynamic correlation, which would be
    possible to compute using conventional methods since it would require more bits to represent the solution than there are molecules in the universe.}
  \label{fig:brain_plots}
\end{figure}
